\documentclass{article}
\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{xcolor}
\usepackage{algcompatible}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{float}
\usepackage{nameref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{authblk}
\usepackage{bm}

\title{\textbf{AMMM Final Project Report}}

%\author{123(\href{mailto:@estudiantat.upc.edu}{Email})
%\and 123(\href{mailto:@estudiantat.upc.edu}{Email})}
\author[1]{Elly}
\author[2]{Jose}

\affil[1]{MIRI \href{mailto:@estudiantat.upc.edu}{@estudiantat.upc.edu}}
\affil[2]{MIRI \href{mailto:@estudiantat.upc.edu}{@estudiantat.upc.edu}}


\begin{document}
\maketitle


\tableofcontents

\newpage

\section{Martian Network Destruction Problem Statement}

The Martian Network Destruction problem can be formally stated as follows:\\
\\
\textbf{\textit{Given}}:
\begin{itemize}
    \item The set $B = \{1, 2, \ldots, n\}$ of Martian military bases. For each pair of bases $i, j \in B$, the number of specialist hours $t_{ij}$ required to destroy the pipe between them is specified (where $t_{ij} = 0$ or $t_{ij} = -1$ indicates that no pipe exists between the two bases $i$ and $j$).

    \item The set $S = \{1, 2, \ldots, m\}$ of specialists. For each specialist $k \in S$, the available working hours $w_k$ and the cost per assignment $c_k$ are specified.
\end{itemize}

\textbf{\textit{Find:}}
\begin{itemize}
    \item Each specialist can be assigned to at most one pipe.

    \item Each pipe we want to destroy must receive enough specialist hours to reach its destruction requirement $t_{ij}$.

    \item The destruction of pipes must create a disconnected network (the graph becomes non-connected, preventing fuel from transporting across all bases).
\end{itemize}

\textbf{\textit{Objective}}:
\begin{itemize}
    \item Minimize the total cost of specialist assignments.
\end{itemize}


\section{ILP Model Formulation}

This problem can be modeled as an Integer Linear Program. To achieve this, the following sets and parameters are defined:\\
\\
\textit{B} \hspace{1.3cm} Set of n bases, index i, j. \\
\textit{S} \hspace{1.3cm} Set of m specialists, index s. \\
\textit{E} \hspace{1.3cm} Set of edges (pipelines) between bases. \\
\textit{$w_s$} \hspace{1.15cm} Number of working hours of specialist s. \\
\textit{$c_s$} \hspace{1.25cm} Cost of using specialist s. \\
\textit{$t_{ij}$} \hspace{1.25cm} Hours required to destroy the pipeline between bases i and j. \\
\\
The following decision variables are also defined:\\
\\
\textit{$x_{se}$} \hspace{1.15cm} Binary. Equal to 1 if specialist s is assigned to edge e; 0 otherwise. \\
\textit{$d_e$} \hspace{1.25cm} Binary. Equal to 1 if edge (pipeline) e is destroyed; 0 otherwise. \\
\textit{$g_i$} \hspace{1.3cm} Binary. Equal to 1 if base i belongs to group 1; 0 if it belongs to group 0. \\
\\
Finally, the ILP model for the pipe destruction problem is as follows:
\begin{equation}
    \textrm{minimize} \quad \sum_{s \in S} \sum_{e \in E} c_s \cdot x_{se}
\end{equation}
subject to:
\begin{equation}
    \sum_{e \in E} x_{se} \leq 1 \qquad \forall s \in S
\end{equation}
\begin{equation}
    \sum_{s \in S} w_s \cdot x_{se} \geq t_{ij} \cdot d_e \qquad \forall e = (i,j) \in E
\end{equation}
\begin{equation}
    x_{se} \leq d_e \qquad \forall s \in S, \forall e \in E
\end{equation}
\begin{equation}
    d_e \geq g_i - g_j \qquad \forall e = (i,j) \in E
\end{equation}
\begin{equation}
    d_e \geq g_j - g_i \qquad \forall e = (i,j) \in E
\end{equation}
\begin{equation}
    1 \leq \sum_{i \in B} g_i \leq n-1
\end{equation}
\\


\section{Heuristics Method}

\subsection{Greedy Method}

\subsubsection{Variable Declaration}

\textbf{Phase 1: Minimum Cut Variables}
\begin{itemize}
    \item $Bases$: Set of bases in the network.
    \item $Pipes$: Set of all pipes connecting bases.
    \item $Demand_p$: The demand (flow requirement) for pipe $p$.
    \item $Partition$: Binary assignment of bases to groups $\{0, 1\}$. Equal to 0 if base $i$ belongs to group 0, 1 otherwise.
    \item $CutPipes$: Set of pipes crossing the partition, i.e., pipes $p = \langle i,j \rangle$ where $Partition[i] \neq Partition[j]$.
\end{itemize}

\textbf{Phase 2: Specialist Assignment Variables}
\begin{itemize}
    \item $Specialists$: Set of available specialists.
    \item $Capacity_s$: The capacity (work units) that specialist $s$ can provide.
    \item $Cost_s$: The cost of hiring specialist $s$.
    \item $CostEffectiveness_s$: Ratio $Cost_s / Capacity_s$ for specialist $s$.
    \item $Solution$: Set of assignments $\langle s, p \rangle$. Each specialist can be assigned to at most one pipe.
    \item $AssignedSpecialists$: Set of specialists currently assigned in the $Solution$.
    \item $RemainingDemand_p$: Uncovered demand for pipe $p$ after current assignments.
\end{itemize}

\subsubsection{Greedy Cost Function}

Our greedy approach operates in two sequential phases:
\\[0.2cm]

\textbf{Phase 1: Minimum Cut Computation}
\\[0.2cm]
We found two greedy algorithms to find the minimum cut partition of the network:

\begin{enumerate}
    \item \textbf{Karger's Algorithm} (randomized): Repeatedly contracts random edges weighted by demand until two super-nodes remain. The algorithm runs multiple iterations to increase the probability of finding the true minimum cut.  This algorithm is faster for sparse graphs, probabilistic guarantee

    \item \textbf{Stoer-Wagner Algorithm} (deterministic): Uses maximum adjacency ordering to systematically find the global minimum cut through a series of min-cut phases.
    This algorithm is better for dense graphs.
    \\[0.2cm]
    The choice of the algorithm can be made in config.dat with minCut.
\end{enumerate}

Both algorithms minimize the total demand in terms of hours crossing the partition:

\begin{equation}
\text{MinCut} = \min_{\text{Partition}} \sum_{p \in \text{Pipes}} \text{Demand}_p \times \mathbb{1}[\text{Partition}[\text{base}_i(p)] \neq \text{Partition}[\text{base}_j(p)]]
\end{equation}

The output is a binary partition that defines which pipes must be covered by specialists (the $CutPipes$).
\\[0.5cm]

We decided to select Karger's algorithm because sometimes the min-cut can be unfeasible while another cut with larger cost can give a feasible output...
\\[0.5cm]

\textbf{Phase 2: Greedy Specialist Assignment}
\\[0.2cm]
For the set of $CutPipes$ identified in Phase 1, we iteratively assign specialists using a greedy cost-effectiveness criterion:

\begin{displaymath}
    q(\langle s, p \rangle, \text{Solution}) = \begin{cases}
    \text{CostEffectiveness}_s & \text{if assigning } s \text{ to } p \text{ is feasible}\\
    +\infty & \text{otherwise}
    \end{cases}
\end{displaymath}

We always select the specialist-pipe pair with the \textbf{lowest cost-effectiveness} (most efficient specialist) among those that:
\begin{enumerate}
    \item Have not been assigned yet
    \item Can contribute to covering the remaining demand of pipe $p$
\end{enumerate}

The assignment continues until all pipes in $CutPipes$ are fully covered or the problem becomes infeasible.

\subsubsection{Pseudocode}

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\caption{Greedy Algorithm}
\begin{algorithmic}
\Statex
\Statex \textbf{PHASE 1: MINIMUM CUT}
\Function{ComputeMinCut}{$Bases$, $Pipes$}
\If{$minCutAlgorithm = \text{"Karger"}$} \Comment{Karger}
    % \State $iterations \gets \max(10, \lfloor(|Bases|^2 \times \ln(|Bases|)) / 2\rfloor)$
    \State $iterations \gets 1$
    \State $cutWeight, Partition \gets \text{Karger}(Bases, Pipes, iterations)$
\Else \Comment{Stoer-Wagner}
    \State $cutWeight, Partition \gets \text{StoerWagner}(Bases, Pipes)$
\EndIf
\State $CutPipes \gets \{p \in Pipes \mid Partition[base_i(p)] \neq Partition[base_j(p)]\}$
\State \Return $CutPipes$
\EndFunction
\Statex
\Statex \textbf{PHASE 2: GREEDY SPECIALIST ASSIGNMENT}
\Function{ValidateAssignment}{$Solution$, $p$}
\State $coveredCapacity \gets \sum_{s \text{ assigned to } p} Capacity_s$
\If{$coveredCapacity \geq Demand_p$}
    \State \Return True
\Else
    \State \Return False
\EndIf
\EndFunction
\Statex
\State $Solution \gets \phi$
\State $AssignedSpecialists \gets \phi$
\State $CutPipes \gets \text{ComputeMinCut}(Bases, Pipes)$
\Statex
% \State \Comment{Sort pipes by demand (descending) - hardest first}
\State $SortedPipes \gets \text{Sort}(CutPipes, key=Demand, reverse=\text{True})$
\Statex
% \State \Comment{Sort specialists by cost-effectiveness (ascending) - best first}
\State $SortedSpecialists \gets \text{Sort}(Specialists, key=CostEffectiveness)$
\Statex
\For{each $p \in SortedPipes$}
    \State $RemainingDemand_p \gets Demand_p$
    \While{$RemainingDemand_p > 0$}
        \State \Comment{Find best available specialist}
        \State $s \gets \arg\min_{s' \in SortedSpecialists \land s' \notin AssignedSpecialists} CostEffectiveness_{s'}$
        \If{$s = \text{NULL}$}
            \State \Return \textsc{Infeasible} \Comment{No specialists available}
        \EndIf
        \State \Comment{Assign specialist s to pipe p}
        \State $Solution \gets Solution \cup \{\langle s, p \rangle\}$
        \State $AssignedSpecialists \gets AssignedSpecialists \cup \{s\}$
        \State $RemainingDemand_p \gets RemainingDemand_p - Capacity_s$
    \EndWhile
    \State \Comment{Verify pipe p is covered}
    \If{\textbf{not} \Call{ValidateAssignment}{$Solution, p$}}
        \State \Return \textsc{Infeasible}
    \EndIf
\EndFor
\State
\Return $Solution$
\end{algorithmic}
\end{algorithm}

\subsubsection{Complexity Analysis}

\textbf{Phase 1 Complexity:}
\begin{itemize}
    \item \textbf{Karger}: $O(k \times m)$ where $k = O(n^2 \log n)$ iterations and $m = |Pipes|$
    \begin{itemize}
        \item Total: $O(n^2 \log n \times m)$
    \end{itemize}
    \item \textbf{Stoer-Wagner}: $O(n \times m + n^2 \log n)$
    \begin{itemize}
        \item More efficient for dense graphs
    \end{itemize}
\end{itemize}

\textbf{Phase 2 Complexity:}
\begin{itemize}
    \item Sorting pipes: $O(p \log p)$ where $p = |CutPipes|$
    \item Sorting specialists: $O(s \log s)$ where $s = |Specialists|$
    \item Assignment loop: $O(p \times s)$ in worst case
    \item \textbf{Total Phase 2}: $O(p \times s + s \log s)$
\end{itemize}

\textbf{Overall Complexity}: $O(n^2 \log n \times m + p \times s)$

% ---------------------------------------------------------------------------------

\subsection{Local Search Method}

\subsubsection{Neighborhood Definition}
We define two complementary neighborhood moves for the Phase~2 resource-allocation sub-problem:

\begin{itemize}
    \item \textbf{Remove:} remove an assigned specialist $s$ from its assigned pipe $p$ when the remaining assigned specialists still provide capacity $\ge$ demand$_p$ (i.e., $p$ remains covered). This strictly reduces cost by $c_s$.
    \item \textbf{Replace:} select an assigned specialist $s_{old}$ on pipe $p$ and replace it with an unassigned specialist $s_{new}$ such that the pipe remains covered after the swap. The move is admissible only if $c_{s_{new}} < c_{s_{old}}$ (otherwise it cannot reduce cost).
\end{itemize}

\subsubsection{Exploration Strategy}

The local search composes the two neighborhoods according to configuration:

\begin{itemize}
    \item If the strategy is \texttt{Both}, apply a Remove phase first (greedy removal of expensive, redundant specialists), then a Replace phase to attempt cost-reducing swaps.
    \item If the strategy is \texttt{Remove} or \texttt{Replace}, explore only the selected neighborhood.
\end{itemize}

Within each neighborhood we support two policies:

\begin{itemize}
    \item \textbf{FirstImprovement}: accept the first strictly improving neighbor found.
    \item \textbf{BestImprovement}: scan the neighborhood and accept the best-improving neighbor.
\end{itemize}

The search repeats until no improving neighbor is found or a stopping criterion (time or iteration limit) is met.

\subsubsection{Pseudocode}

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\caption{Local Search}
\begin{algorithmic}
\Function{LocalSearch}{$solution, policy, neighborhoodStrategy, endTime, maxIterations$}
\State $incumbent \gets solution$
    \State $incumbentCost \gets incumbent.getFitness()$
    \State $iter \gets 0$
    \While{$time < endTime$ \textbf{and} $iter < maxIterations$}
        \State $iter \gets iter + 1$
        \If{$neighborhoodStrategy == "Both"$}
            \State $neighbor \gets ExploreRemove(incumbent, policy)$
            \If{$neighbor.getFitness() < incumbentCost$}
                \State $incumbent \gets neighbor;$
                \State $incumbentCost \gets neighbor.getFitness();$
            \EndIf
            \Statex
            \State $neighbor \gets ExploreReplace(incumbent, policy)$
            \If{$neighbor.getFitness() < incumbentCost$}
                \State $incumbent \gets neighbor;$
                \State $incumbentCost \gets neighbor.getFitness();$
            \EndIf
        \Statex
        \ElsIf{$neighborhoodStrategy == "Remove"$}
            \State $neighbor \gets ExploreRemove(incumbent, policy)$
            \If{$neighbor.getFitness() < incumbentCost$}
                \State $incumbent \gets neighbor;$
                \State $incumbentCost \gets neighbor.getFitness();$
            \EndIf
        \Else
            \State $neighbor \gets ExploreReplace(incumbent, policy)$
            \If{$neighbor.getFitness() < incumbentCost$}
                \State $incumbent \gets neighbor;$
                \State $incumbentCost \gets neighbor.getFitness();$
            \EndIf
        \EndIf
        \Statex
        \If{$neighbor.getFitness() > incumbentCost$} \textbf{break} \Comment{Local optimum reached}
        \EndIf
    \EndWhile
    \Statex
    \State \Return incumbent
\EndFunction
\end{algorithmic}
\end{algorithm}

% \subsubsection{ExploreRemove}
% - Iterate assigned specialists in descending cost order.
% - For each specialist $s$: if \texttt{canRemoveSpecialist(s)} is true, create neighbor = clone, unassign $s$, evaluate; if cost decreases then accept per policy (First/Best).

% \subsubsection{ExploreReplace}
% - Let \texttt{assigned} be assigned specialists sorted by cost descending; \texttt{unassigned} be unassigned specialists sorted by cost ascending.
% - For each $s_{old}$ in \texttt{assigned}:
%   - Let $p \gets$ assigned pipe of $s_{old}$ and $excess \gets$ excess capacity at $p$.
%   - For each $s_{new}$ in \texttt{unassigned} with $c_{s_{new}} < c_{s_{old}}$:
%     - Compute $newExcess = excess - cap(s_{old}) + cap(s_{new})$.
%     - If $newExcess \ge 0$ then neighbor = clone, unassign $s_{old}$, assign $s_{new}$ to $p$, evaluate; accept per policy if cost improves.

% \subsubsection{Stopping Criteria}
% The search stops when one of:
% - Elapsed time $\ge$ configured time limit.
% - Iterations $\ge$ configured iteration limit.
% - No improving neighbor found.

\subsubsection{Complexity Analysis}

% We rely on the following Solution API operations: \texttt{getAssignedSpecialists()}, \texttt{getUnassignedSpecialists()}
% - \texttt{getAssignedPipe(specId)}, \texttt{canRemoveSpecialist(specId)}
% - \texttt{getExcessCapacity(pipeId)} (assigned capacity minus demand)
% - \texttt{clone()}, \texttt{assign(specId, pipeId)}, \texttt{unassign(specId)}, \texttt{evaluate()}, \texttt{getFitness()}

Complexity per neighborhood exploration is dominated by iterating assigned/unassigned specialists and evaluating candidate neighbors; with $S$ specialists and $P$ cut pipes a full scan is $O(S^2 + P\cdot S)$ in the worst case, but practical pruning (sorting by cost, early acceptance under FirstImprovement) reduces the observed cost.

% ---------------------------------------------------------------------------------

\subsection{GRASP Method}

\subsubsection{High-level description}
GRASP (Greedy Randomized Adaptive Search Procedure) performs repeated constructive phases followed by local search. Each constructive phase builds a feasible solution by iteratively assigning specialists to cut pipes using a restricted candidate list (RCL) controlled by parameter $\alpha \in [0,1]$: $\alpha = 0$ $\Rightarrow$ purely greedy, $\alpha = 1$ $\Rightarrow$ pure random (within admissible candidates).

After construction, the candidate solution is improved using the Local Search described above. The best solution over all GRASP iterations is returned.

\subsubsection{Construction phase}
Per pipe (processed in order of decreasing remaining demand), we:

\begin{itemize}
    \item Compute the list of available specialists that can contribute to the pipe.
    \item Sort available specialists by cost-effectiveness $ce(s) = c_s / cap_s$ (lower = better).
    \item Let $ce_{best}$ and $ce_{worst}$ be the best and worst cost-effectiveness in the available list.
    \item Define threshold $T = ce_{best} + \alpha \cdot (ce_{worst} - ce_{best})$.
    \item Build RCL = $\{ s \mid ce(s) \le T \}$ (if empty, use the best specialist).
    \item Randomly pick $s$ from RCL and assign to the pipe; repeat until the pipe is covered or no specialists remain.
\end{itemize}

This adaptive RCL balances greediness and diversification.

\subsubsection{Pseudocode FIXX}

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\caption{GRASP Construction Phase}
\begin{algorithmic}

\State $Solution \gets \phi$
\State $CoveredMembers \gets \phi$
\State $CandidatePairs \gets \{<i,j> \mid i,j \in Members \quad \textrm{and} \quad Bids_{ij} + Bids_{ji} \neq 0\}$
\State $Priority(i,j) \gets 0 \quad \forall <i,j> \in CandidatePairs$
\While{$CandidatePairs \neq \phi$}
    \State Evaluate $q(<i',j'>, Solution) \quad \forall <i',j'> \in CandidatePairs$
    \State $CandidatePairs \gets \{<i',j'> \in CandidatePairs \mid q(<i',j'>,S) > 0\}$
    \State \textcolor{red}{$q^{min} \gets \textrm{min}\{q(<i',j'>,Solution) \mid <i',j'> \in CandidatePairs\}$} \Comment{RCL Procedure}
    \State \textcolor{red}{$q^{max} \gets \textrm{max}\{q(<i',j'>,Solution) \mid <i',j'> \in CandidatePairs\}$}
    \State \textcolor{red}{$\textrm{RCL}_{max} \gets \{<i',j'> \in CandidatePairs \mid q(<i',j'>, Solution) \geq q^{max} - \alpha(q^{max} - q^{min}) \}$}
    \State \textcolor{red}{$<i,j> \gets \textrm{ select} <i',j'> \in \textrm{RCL}$ at random}
    \State $CandidatePairs \gets CandidatePairs \setminus \{<i,j>, <j,i>\}$
    \State $CoveredMembers \gets CoveredMembers \cup \{i,j\}$
    \State $Solution \gets Solution \cup \{<i,j>\}$
    \State $Priority(<i,j>) \gets 1$
\EndWhile
\State \Return $Solution$

\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{GRASP Main Loop}
\begin{algorithmic}
\Function{GRASP}{maxIterations, $\alpha$, localSearchConfig}
    \State best $\gets$ infeasible-solution (sentinel with cost $+\infty$)
    \For{iter = 1 \textbf{to} maxIterations}
        \State partition $\gets$ ComputeMinCut()
        \State cutPipes $\gets$ pipes crossing partition
        \State solution $\gets$ ConstructSolution($\alpha$, partition, cutPipes)
        \If{solution.isFeasible() \textbf{and} localSearchConfig.enabled}
            \State solution $\gets$ LocalSearch(solution, localSearchConfig)
        \EndIf
        \If{solution.isFeasible() \textbf{and} solution.getFitness() < best.getFitness()}
            \State best $\gets$ solution
        \EndIf
        \If{time limit reached} \textbf{break}
    \EndFor
    \State \Return best
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsubsection{Parameter tuning and practical notes}
- Choose $\alpha$ by tuning; typical values are in $[0.0,0.3]$ for problems where greedy guidance is strong.
- Number of GRASP iterations trades time for solution quality; stop early when time budget is exhausted.
- Always compute the min-cut once per GRASP iteration (the partition affects which pipes must be covered).
- Use Local Search after each constructive phase when computational budget allows; Local Search provides substantial improvements.

\subsubsection{Complexity}
Each GRASP iteration performs one constructive pass (roughly $O(p\cdot s + s\log s)$) and an optional local search whose cost depends on the configured neighborhood policy and limits. Overall runtime is linear in the number of iterations and dominated by Local Search when enabled.


% \subsection{Local Search Method}

% \subsubsection{Neighborhood}

% The neighborhood of this conflict resolution problem is defined as the solution obtained by replacing the member pair $<i,j>$ currently not included in the solution (indicated by $Priority(<i,j>)$ = 0) with its flipped counterpart $<j,i>$ included in the solution (indicated by $Priority(<j,i>)$ = 1), if $Bids_{ij} > Bids_{ji} \quad \forall i,j \in Members$.

% \subsubsection{Exploration Strategy}

% Based on the neighborhood mentioned above, the replacing procedure may necessitate the flipping of other pairs as a knock-on effect. If the total decrease in bids from passively flipped pairs (defined as \textbf{\textit{knock-on flipped pairs}}, represented by \bm{$edges^{flip}$}) is less than the increase from the actively flipped pair $<i,j>$, we achieve a better solution.\\
% For example, if we have $(Bids_{ij} > Bids_{ji}$ and $<j,i> \in Solution$ (which indicates that $Priority(<j,i>) = 1$), when we consider replacing $<j,i>$ with $<i,j>$ in the current solution, some priority cycles may be formed. To address this, we need to develop a strategy for identifying pairs to flip within this directed graph, ensuring that no cycles remain.\\
% First, we reverse the pair (representing the edges in the directed graph) from $<j, i>$ to $<i, j>$ in the current solution (representing the vertices in the directed graph). We then proceed to eliminate all edges with an indegree of 0 or an outdegree of 0, ensuring that all remaining edges in the graph are part of a cycle.\\
% Once we have the remaining edges $edges^{remain}$, we utilize equation $max(q(<i,j'>, edges^{flip}))$ to continuously select edge $<i',j'>$ and added to $edges^{flip}$ until no cycles are left in the graph. We prioritize edges $<i', j'>$ with higher indegree and outdegree, as we believe such edges are more capable of eliminating multiple cycles compared to others. If multiple edges are tied, we will select the edge with the lowest bid decrease ($Bids_{i',j'} - Bids_{j'i'}$).The $edges^{flip}$ cost function is defined as follows.\\
% \newpage

% $q(<i',j'>, edges^{flip})$=\\
% \\
% \begin{displaymath}
%     \begin{cases}
%     -1 & \\
%     \qquad\quad\textrm{if} \quad Bids_{i'j'} - Bids_{j'i'} + \sum_{<i'',j''> \in edges^{flip}} Bids_{i''j''} - Bids{j''i''} \geq Bids_{ij} - Bids_{ji}\\
%     \qquad\quad\quad\textrm{or } edges^{remain} \mid edges^{flip} = edges^{remain} \mid edges^{flip} \cup \{<i',j'>\})\\
%     \\
%     \sum_{k' \in \{i',j'\}} indegree(k') + outdegree(k') & \\
%     \\
%     \qquad\quad\textrm{if} \quad Bids_{i'j'} - Bids_{j'i'} + \sum_{<i'',j''> \in edges^{flip}} Bids_{i''j''} - Bids{j''i''} < Bids_{ij} - Bids_{ji}\\
%     \qquad\quad\quad\textrm{and } edges^{remain} \mid edges^{flip} > edges^{remain} \mid edges^{flip} \cup \{<i',j'>\}
%     \end{cases}
% \end{displaymath}
% \\
% Finally, we check whether flipping every knock-on edge $<i',j'> \in edges^{flip}$ will create any cycle in the graph. If there are no cycles formed, we can replace the pair $<i,j>$ in the current solution. This change will yield a better solution with the objective value calculated as follows: $Objective + (Bids_{ij} - Bids_{ji}) - \sum_{<i',j'> \in edges^{flip}} Bids_{i'j'} - Bids_{j'i'}$.\\
% \\
% \textbf{\textit{We continue executing the above procedure until no improvements are reached.}}

% \subsubsection{Variable Declaration} \label{ls_declaration}

% Alongside the variables established in the Greedy Method \ref{declaration}, additional auxiliary variables for the local search procedure are defined as follows:
% \begin{itemize}
%     \item $pairsWithHigherBid$: Member pair $<i,j>$ not included in solution but having higher bid than their flipped counterpart $<j,i>$ included in solution.
%     \item $edges^{flip}$: Set of member pairs needed to be flipped if member pair in $pairsWithHigherBid$ requires flipping.
% \end{itemize}

% \subsubsection{Pseudocode}

% \begin{algorithm}[H]
% \renewcommand{\thealgorithm}{}
% \caption{Local Search Algorithm (Part 1: Auxiliary functions)}
% \begin{algorithmic}

% \Function{FlipPairWithImprovement}{$<i,j>$}
%     \State $bidIncrease \gets Bids_{ij} - Bids_{ji}, $
%     \State $potentialSolution \gets solution$
%     \State $potentialSolution[potentialSolution.\textrm{INDEX}(<j,i>)] \gets <i,j>$
%     \State $edges, indegree, outdegree \gets TrimGraph(potentialSolution)$
%     \If{$edges = \phi$}
%         \State \Return True, $bidIncrease, \phi$
%     \EndIf
%     \State $edges^{flip}, bidDecrease \gets GetKnockonFlippedPairs(bidIncrease, edges, indegree, outdegree)$
%     \If{$bidDecrease = -1$}
%         \State \Return False, 0, $\phi$
%     \EndIf
%     \If{$CanBeFlipped(<i,j>, edges^{flip}) = $True}
%         \State \Return True, $bidIncrease - bidDecrease, edges^{flip}$
%     \EndIf
%     \State \Return False, 0, $\phi$
% \EndFunction

% \algstore{local_search}
% \end{algorithmic}
% \end{algorithm}
% \newpage

% \begin{algorithm}[]
% %\renewcommand{\thealgorithm}{}
% %\caption{Local Search Algorithm (Part 1: Auxiliary functions)}
% \begin{algorithmic}
% \algrestore{local_search}

% \Function{CanBeFlipped}{$<i,j>, edges^{flip}$}
%     \State $potentialSolution \gets currentSolution$
%     \State $potentialSolution[potentialSolution.\textrm{INDEX}(<j,i>)] \gets <i,j>$
%     \For{\textbf{each} $<i',j'> \in edges^{flip}$}
%         \State $potentialSolution[potentialSolution.\textrm{INDEX}(<i',j'>)] \gets <j',i'>$
%     \EndFor
%     \State $edges \gets TrimGraph(potentailSolution)$
%     \If{$edges \neq \phi$}
%     \State \Return False
%     \EndIf
%     \State \Return True
% \EndFunction

% \Statex

% \Function{GetKnockonFlippedPairs}{$bidIncrease$, $solution$, $indegree$, $outdegree$}
% \State $totalBidDecrease, edges^{flip} \gets 0, \phi$
% \While{$edges^{remain} \neq \phi$}
% \State $edges^{candidate} \gets \{<i,j> \in edges^{remain} \mid Bids_{ij} - Bids_{ji} + totalBidDecrease < bidIncrease\}$
% \If{$edges^{candidate} = \phi$}
%     \State \Return $\phi, -1$
% \EndIf
% \State $vertices \gets GetVerticesFromEdges(edges)$
% \State $edgeDegrees(<i',j'>) \gets \sum_{k' \in {i',j'}} indegree(k') + outdegree(k') \quad \forall <i',j'> \in edges^{remain}$
% \State $sortedEdges^{candidate} \gets \textrm{SORT}$(
% \State \qquad $edges^{candidate}, (vertexDegrees(<i',j'>), Bids_{j'i'} - Bids_{i'j'}), DESC)$
% \State $foundCandidate \gets \textrm{FALSE}$
% \For{\textbf{each} $<i',j'> \in edges^{candidate}$}
% \State $edges^{remain'} \gets edges^{remain}$
% \State $edges^{remain'}[edges^{remain'}.\textrm{INDEX}(<i',j'>)] \gets <j',i'>$
% \State $edges^{remain'}, indegree, outdegree \gets TrimGraph(edges^{remain'})$
% \If{$edges^{remain'} \subset edges^{remain}$}
% \State $totalBidDecrease \gets totalBidDecrease + Bids_{i'j'} - Bids_{j'i'}$
% \State $edges^{remain} \gets edges^{remain'}$
% \State $edges^{flip} \gets edges^{flip} \cup \{{i',j'}\}$
% \State $foundCandiate \gets$ True
% \State \textbf{break}
% \EndIf
% \EndFor
% \If{$foundCandidate = \textrm{FALSE}$}
% \State \Return $\phi, -1$
% \EndIf
% \EndWhile
% \State \Return $edges^{flip}, totalBidDecrease$
% \EndFunction

% \end{algorithmic}
% \end{algorithm}

% \begin{algorithm}[H]
% \renewcommand{\thealgorithm}{}
% \caption{Local Search Algorithm (Part 2: Main Algorithm)}
% \begin{algorithmic}

% \State $Solution \gets GreedyConstructionPhase()$
% \State $improved \gets$ True
% \While{$improved$}
%     \State $improved \gets$ False
%     \State $pairsWithHigherBids \gets \{<i,j> \mid <j,i> \in Solution \textrm{ and } Bids_{ij} > Bids_{ji}\}$
%     \For{\textbf{each} $<i,j> \in pairsWithHigherBids$}
%         \State $canBeFlipped, bidIncrease, edges^{flip} \gets FlipPairWithImprovement(<i,j>)$
%         \If{$canBeFlipped = $ True}
%             \State $improved \gets$ True
%             \For{\textbf{each} $<i^{'}, j^{'}> \in edges^{flip} \cup \{ <j,i>\}$}
%                 \State $Solution[Solution.\textrm{INDEX}(<i^{'}, j^{'}>)] \gets <j^{'}, i^{'}>$
%                 \State $Priority(<i',j'>) \gets 0$
%                 \State $Priority(<j',i'>) \gets 1$
%             \EndFor
%         \EndIf
%     \EndFor
% \EndWhile
% \State \Return $Solution$

% \end{algorithmic}
% \end{algorithm}

% %\newpage

% \subsection{GRASP Method}
% \subsubsection{Variable Declaration}
% The same as \ref{ls_declaration}.

% \subsubsection{Pseudocode}

% \begin{algorithm}[H]
% \renewcommand{\thealgorithm}{}
% \caption{GRASP Construction Phase}
% \begin{algorithmic}

% \State $Solution \gets \phi$
% \State $CoveredMembers \gets \phi$
% \State $CandidatePairs \gets \{<i,j> \mid i,j \in Members \quad \textrm{and} \quad Bids_{ij} + Bids_{ji} \neq 0\}$
% \State $Priority(i,j) \gets 0 \quad \forall <i,j> \in CandidatePairs$
% \While{$CandidatePairs \neq \phi$}
%     \State Evaluate $q(<i',j'>, Solution) \quad \forall <i',j'> \in CandidatePairs$
%     \State $CandidatePairs \gets \{<i',j'> \in CandidatePairs \mid q(<i',j'>,S) > 0\}$
%     \State \textcolor{red}{$q^{min} \gets \textrm{min}\{q(<i',j'>,Solution) \mid <i',j'> \in CandidatePairs\}$} \Comment{RCL Procedure}
%     \State \textcolor{red}{$q^{max} \gets \textrm{max}\{q(<i',j'>,Solution) \mid <i',j'> \in CandidatePairs\}$}
%     \State \textcolor{red}{$\textrm{RCL}_{max} \gets \{<i',j'> \in CandidatePairs \mid q(<i',j'>, Solution) \geq q^{max} - \alpha(q^{max} - q^{min}) \}$}
%     \State \textcolor{red}{$<i,j> \gets \textrm{ select} <i',j'> \in \textrm{RCL}$ at random}
%     \State $CandidatePairs \gets CandidatePairs \setminus \{<i,j>, <j,i>\}$
%     \State $CoveredMembers \gets CoveredMembers \cup \{i,j\}$
%     \State $Solution \gets Solution \cup \{<i,j>\}$
%     \State $Priority(<i,j>) \gets 1$
% \EndWhile
% \State \Return $Solution$

% \end{algorithmic}
% \end{algorithm}


% \begin{algorithm}[H]
% \renewcommand{\thealgorithm}{}
% \caption{GRASP Procedure}
% \begin{algorithmic}

% \State $Object^{best}, Solution^{best} \gets 0, \phi$
% \For{$retry = \textrm{1 to MaxIterations}$}
% \State $Obejctive, Solution \gets 0, \phi$
% \State $Solution \gets doConstructionPhase()$
% \State $Solution \gets doLocalSearchPhase(Solution)$
% \If{$Obejctive > Objective^{best}$}
% \State $Objective^{best} \gets Obejctive$
% \State $Solution^{best} \gets Solution$
% \EndIf
% \EndFor
% \State \Return $Solution^{best}$

% \end{algorithmic}
% \end{algorithm}

\section{Experiment Result Analysis}

\subsection{Experiment Dataset And Environment}

We generated several datasets of different sizes. datasets are prefixed by sXXXX\_pXXXX; e.g s100\_p100 means 100 specialists and 100 pipes.
These experiments were conducted on an Apple MacBook Pro laptop with an Apple M4 chip and 32GB of memory. Solving times may vary slightly on other computers, particularly for the ILP model.


\subsection{Parameter Tuning For GRASP}

We tested \bm{$\alpha$} from 0 to 1 in increments of 0.1, using datasets with 100 specialist and 1000 pipes without conducting the local search procedure, and the maximum iterations for the constructive phase is set to 100.  For the results, we selected the best mean objective with the least standard deviation (risk-adjusted formula) over 100 runs per alpha value.

\begin{figure}[H]
\begin{tikzpicture}
\begin{axis}[
    title={\textbf{Quality of Solutions (Risk-Adjusted: Mean + SD)}},
    xlabel=\bm{$\alpha$},
    ylabel=\textbf{\textit{Score (Mean + SD)}},
    xmin=0, xmax=1,
    ymin=2000, ymax=16000,
    xtick=data,
    ytick={2000, 4000, 6000, 8000, 10000, 12000, 14000, 16000},
    ymajorgrids=true,
    grid style=dashed,
    width=0.7\textwidth,
    legend pos=outer north east,
    legend style={nodes={scale=1, transform shape}}
]

\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_0.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_1.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_2.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_3.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_4.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_5.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_6.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_7.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_8.csv};
\addplot table[x=alpha, y expr=\thisrow{mean_objective} + \thisrow{std_objective}, col sep=comma] {s100_p1000_grasp_tuning/s100_p1000_instance_9.csv};

\legend{instance\_0 ($\alpha=0.1$),instance\_1 ($\alpha=0.1$),instance\_2 ($\alpha=0.1$),instance\_3 ($\alpha=0.3$),instance\_4 ($\alpha=0.2$),instance\_5 ($\alpha=0.0$),instance\_6 ($\alpha=0.3$),instance\_7 ($\alpha=0.2$),instance\_8 ($\alpha=0.2$),instance\_9 ($\alpha=0.2$)}

\end{axis}
\end{tikzpicture}
\captionsetup{labelformat=empty}
\caption{Figure 4.1}
\label{fig:fig41}
\end{figure}

\noindent As shown in figure \nameref{fig:fig41}, a better solution is most likely achieved when \bm{$\alpha$} is set from 0.1 to 0.2. \textbf{In the following experiments, we will set \bm{$\alpha$} equal to 0.15 when conducting the GRASP method to give a good balance between quality and randomness}.


\subsection{Solving Time}

As shown in \nameref{fig:fig42} the ILP model takes approximately X to Y minutes to reach the optimal solution, while the Greedy method requires less than 200 milliseconds. This means the Greedy method is roughly 10000 times faster than the ILP model. \\
The Local Search method takes about 20 seconds to solve the problem.
Additionally, when GRASP is executed with 10 iterations and followed by the Local Search procedure, it takes about ten times longer than the Local Search method alone. \\
Furthermore, when GRASP is executed with 100 iterations and not followed by the Local Search procedure, it takes around 25 seconds to solve the problem.\\
As demonstrated in \nameref{fig:fig43}, the time required to solve the ILP model varies significantly. At times, we may be fortunate enough to obtain the optimal solution quickly. Specifically, if the number of members is small (fewer than 42), we can effectively use the ILP model to achieve the optimal solution.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    title={\textbf{Solving Time ($\mathbf{S=100}, \mathbf{P=1000}$)}},
    xlabel={Instance},
    ylabel={\textbf{Solving Time} ($\mathbf{s}$)},
    grid=major,
    width=\textwidth,
    legend pos=outer north east,
    ybar,
    bar width=5pt,
    % enlarge x limits=0.15,
    xtick={0, 1, 2, 3, 4, 5, 6, 7, 8, 9},
    ymode=log,
    log origin=infty,
    width=0.9\textwidth,
]

\addplot[fill=green, bar shift=-10pt] table[col sep=comma, x expr=0, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_0.csv};
\addplot[fill=yellow, bar shift=-5pt] table[col sep=comma, x expr=0, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_0.csv};
\addplot[fill=blue, bar shift=0pt] table[col sep=comma, x expr=0, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_0.csv};
\addplot[fill=red, bar shift=5pt] table[col sep=comma, x expr=0, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_0.csv};
\addplot[fill=brown, bar shift=10pt] table[col sep=comma, x expr=0, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_0.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=1, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_1.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=1, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_1.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=1, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_1.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=1, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_1.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=1, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_1.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=2, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_2.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=2, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_2.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=2, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_2.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=2, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_2.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=2, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_2.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=3, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_3.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=3, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_3.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=3, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_3.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=3, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_3.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=3, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_3.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=4, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_4.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=4, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_4.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=4, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_4.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=4, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_4.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=4, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_4.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=5, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_5.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=5, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_5.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=5, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_5.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=5, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_5.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=5, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_5.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=6, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_6.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=6, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_6.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=6, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_6.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=6, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_6.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=6, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_6.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=7, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_7.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=7, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_7.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=7, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_7.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=7, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_7.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=7, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_7.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=8, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_8.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=8, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_8.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=8, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_8.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=8, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_8.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=8, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_8.csv};

\addplot[fill=green, forget plot, bar shift=-10pt] table[col sep=comma, x expr=9, y=mean_time] {data/s100_p1000_greedy/s100_p1000_instance_9.csv};
\addplot[fill=yellow, forget plot, bar shift=-5pt] table[col sep=comma, x expr=9, y=mean_time] {data/s100_p1000_grasp/s100_p1000_instance_9.csv};
\addplot[fill=blue, forget plot, bar shift=0pt] table[col sep=comma, x expr=9, y=mean_time] {data/s100_p1000_greedy_ls/s100_p1000_instance_9.csv};
\addplot[fill=red, forget plot, bar shift=5pt] table[col sep=comma, x expr=9, y=mean_time] {data/s100_p1000_grasp_ls/s100_p1000_instance_9.csv};
\addplot[fill=brown, forget plot, bar shift=10pt] table[col sep=comma, x expr=9, y=mean_time] {data/s100_p1000_cplex/s100_p1000_instance_9.csv};

\legend{Greedy, GRASP, Greedy + LS, GRASP + LS, ILP}

\end{axis}
\end{tikzpicture}
\captionsetup{labelformat=empty}
\caption{Figure 4.2: Solving Time for each algorithm}
\label{fig:fig42}
\end{figure}


% \begin{figure}[H]
%
% \begin{tikzpicture}[]
% \begin{axis}[
%     title={\textbf{Solving Time (39 to 45 members)}},
%     x tick label style={
%         /pgf/number format/1000 sep=},
%     ylabel=\textbf{Solving Time } ($\mathbf{s})$,
%     xlabel=\textbf{Members},
%     ybar interval=0.8,
%     xtick=data,
%     bar width = 10pt,
%     ymode=log,
%     ymax=10000,
%     bar shift=0pt,
%     log origin=infty,
%     legend pos=outer north east,
%     width=0.7\textwidth,
%     legend style={nodes={scale=0.8, transform shape}}
% ]
%
%
% \addplot table[
%     header=true,
%     x=id,
%     y=time
% ] {data/variable_members/solving_time_greedy.dat};
%
% \addplot table[
%     header=true,
%     x=id,
%     y=time
% ] {data/variable_members/solving_time_grasp.dat};
%
% \addplot table[
%     header=true,
%     x=id,
%     y=time
% ] {data/variable_members/solving_time_ls.dat};
%
% \addplot table[
%     header=true,
%     x=id,
%     y=time
% ] {data/variable_members/solving_time_grasp_with_ls.dat};
%
%
% \addplot table[
%     header=true,
%     x=id,
%     y=time
% ] {data/variable_members/solving_time_cplex.dat};
%
% \legend{Greedy,GRASP(100 Iter. w/o local search \bm{$\alpha$} = 0.1),Local Search,GRASP(10 Iter. w/ local search \bm{$\alpha$} = 0.1),ILP}
% \end{axis}
% \end{tikzpicture}
% \captionsetup{labelformat=empty}
% \caption{Figure 4.3}
% \label{fig:fig43}
% \end{figure}


\subsection{Solving Quality}

\begin{figure}[H]
\centering

% Build coordinates from individual CSV files
\newcommand{\buildcoords}[2]{%
    \gdef#1{}%
    \pgfplotsforeachungrouped \i in {0,...,9} {%
        \pgfplotstableread[col sep=comma]{data/#2/s100_p1000_instance_\i.csv}\temptable
        \pgfplotstablegetelem{0}{mean_objective}\of\temptable
        \ifx#1\empty
            \xdef#1{(\i,\pgfplotsretval)}%
        \else
            \xdef#1{#1 (\i,\pgfplotsretval)}%
        \fi
    }%
}

\buildcoords{\greedydata}{s100_p1000_greedy}
\buildcoords{\graspdata}{s100_p1000_grasp}
\buildcoords{\greedylsdata}{s100_p1000_greedy_ls}
\buildcoords{\grasplsdata}{s100_p1000_grasp_ls}
\buildcoords{\cplexdata}{s100_p1000_cplex}

\begin{tikzpicture}
\begin{axis}[
    title={\textbf{Quality of Solutions ($\mathbf{S=100}, \mathbf{P=1000}$)}},
    xlabel={\textbf{Instance}},
    ylabel={\textbf{Mean Objective (Cost)}},
    xmin=0, xmax=9,
    ymin=2500, ymax=8000,
    xtick={0, 1, 2, 3, 4, 5, 6, 7, 8, 9},
    ytick={3000, 4000, 5000, 6000, 7000, 8000},
    ymajorgrids=true,
    grid style=dashed,
    width=0.9\textwidth,
    legend pos=outer north east,
    legend style={nodes={scale=0.8, transform shape}}
]

\addplot[green, thick, mark=triangle] coordinates {\greedydata};
\addplot[yellow!80!black, thick, mark=square] coordinates {\graspdata};
\addplot[blue, thick, mark=diamond] coordinates {\greedylsdata};
\addplot[red, thick, mark=o] coordinates {\grasplsdata};
\addplot[brown, thick, mark=star] coordinates {\cplexdata};

\legend{Greedy, GRASP, Greedy + LS, GRASP + LS, ILP (Optimal)}

\end{axis}
\end{tikzpicture}
\captionsetup{labelformat=empty}
\caption{Figure 4.3: Solution Quality for each algorithm}
\label{fig:fig43}
\end{figure}

% \begin{figure}[H]
% \begin{tikzpicture}
% \begin{axis}[
%     title={\textbf{Quality of Solutions (10 datasets with 45 members)}},
%     xlabel=\textbf{{Dataset Number}},
%     ylabel=\textbf{{Total Income}},
%     xmin=1, xmax=10,
%     ymin=4000, ymax=5300,
%     xtick=data,
%     ytick={4000, 4100, 4200,4300,4400,4500,4600,4700,4800,4900,5000,5100,5200,5300},
%     ymajorgrids=true,
%     grid style=dashed,
%     width=0.7\textwidth,
%     legend pos=outer north east,
%     legend style={nodes={scale=0.8, transform shape}}
% ]

% \addplot[green,thick,mark=triangle] table {data/45members/objective_greedy.dat};
% \addplot[blue,thick,mark=triangle] table {data/45members/objective_grasp.dat};
% \addplot[brown,thick,mark=triangle] table {data/45members/objective_ls.dat};
% \addplot[black,thick,mark=triangle] table {data/45members/objective_grasp_with_ls.dat};
% \addplot[red,thick,mark=square*] table {data/45members/objective_cplex.dat};


% \legend{Greedy,GRASP(100 Iter. w/o local search  $\alpha = 0.1$),Local Search,GRASP(10 Iter. w/ local search $\alpha = 0.1$),ILP(Optimal)}

% \end{axis}
% \end{tikzpicture}
% \captionsetup{labelformat=empty}
% \caption{Figure 4.4}
% \label{fig:fig44}
% \end{figure}


% \begin{figure}[H]
% \begin{tikzpicture}
% \begin{axis}[
%     title={\textbf{Quality of Solutions (39 to 45 members)}},
%     xlabel=\textbf{{Members}},
%     ylabel=\textbf{{Total Income}},
%     xmin=39, xmax=45,
%     ymin=3500, ymax=5200,
%     xtick=data,
%     ytick={3500,3600,3700,3800,3900,4000, 4100, 4200,4300,4400,4500,4600,4700,4800,4900,5000,5100,5200},
%     ymajorgrids=true,
%     grid style=dashed,
%     width=0.7\textwidth,
%     legend pos=outer north east,
%     legend style={nodes={scale=0.8, transform shape}}
% ]

% \addplot[green,thick,mark=triangle] table {data/variable_members/objective_greedy.dat};
% \addplot[blue,thick,mark=triangle] table {data/variable_members/objective_grasp.dat};
% \addplot[brown,thick,mark=triangle] table {data/variable_members/objective_ls.dat};
% \addplot[black,thick,mark=triangle] table {data/variable_members/objective_grasp_with_ls.dat};
% \addplot[red,thick,mark=square*] table {data/variable_members/objective_cplex.dat};


% \legend{Greedy,GRASP(100 Iter. w/o local search  $\alpha = 0.1$),Local Search,GRASP(10 Iter. w/ local search $\alpha = 0.1$),ILP(Optimal)}

% \end{axis}
% \end{tikzpicture}
% \captionsetup{labelformat=empty}
% \caption{Figure 4.5}
% \label{fig:fig45}
% \end{figure}

\nameref{fig:fig44} and \nameref{fig:fig45} shows that the Greedy approach yields the worst solution. In contrast, both GRASP (100 iterations without local search) and Local Search provide similar results. Among the heuristic methods, GRASP (10 iterations with local search) offers the best solution.


\subsection{Experiment Conclusion}

If the number of members is small (fewer than 42), we should always use the ILP model to achieve the optimal solution. If the number of members is large (more than 42) and we need a reasonably good solution within a short timeframe, we should apply the GRASP with 10 iterations, followed by a local search procedure. This approach will yield the best solution among the heuristic methods we tested.

\section{Personal Reflections}

Initially, we had limited knowledge of graph theory and were unfamiliar with concepts like topological sorting or directed acyclic graphs. We approached the subject incorrectly at first, but after receiving guidance from our professors and exploring graph theory in more depth, a new world opened up for us. We were amazed by the efficiency of graph algorithms.\\
For us, the optimization methods used in linear programming represent a significant shift in thinking. These methods can be elegant, and we always strive to pursue optimal solutions in theory. However, in practice, solving problems can sometimes be quite costly. Therefore, for these problems we should employ heuristic methods as a tradeoff. It is essential to experiment and iterate in order to discover better solutions.\\
We will continue to refine this project by optimizing the heuristic methods, which we believe will reduce solving time and improve solution quality.


\section{Acknowledgements}

We want to give a big thank you to Prof. Enric Rodriguez and Prof. Luis Velasco for all their guidance and support throughout this report and during the whole course. Your help has truly meant a lot to us!

\newpage
\appendix

\section{Pseudocode of Auxiliary Functions for Directed Graph}


Some auxiliary functions are utilized to process directed graphs for the \textit{Greedy}, \textit{Local Search}, and \textit{GRASP} methods.
\begin{itemize}
    \item The function $TopologicalSort$ implements \textbf{\textit{Kahn's algorithm}} to obtain the topological sort of a directed graph, which has $CoveredMembers$ as vertices and $Solution$ (in Greedy method, it is the partial solution) as edges. If there are edges remaining, this indicates that a cycle exists in the graph.
    \item The function $TrimGraph$ continues to eliminate all vertices with zero indegree or zero outdegree until every remaining edge is part of a cycle.
\end{itemize}

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\caption{Auxiliary functions For Directed Graph}
\begin{algorithmic}

\Function{GetVerticesFromEdges}{$edges$}
\State $vertices \gets \phi$
\For{\textbf{each} $<i,j> \in edges$}
\State $vertices \gets vertices \cup {i, j}$
\EndFor
\State \Return $vertices$
\EndFunction

\Statex

\Function{ConstructNeighbors}{$vertices$, $eges$}
\State $neighbors \gets \phi$
\For{\textbf{each} $<i,j> \in edges$}
\State $neighbors(i) \gets neighbors(i) \cup {j}$
\EndFor
\State \Return $neighbors$
\EndFunction

\Statex

\Function{TopologicalSort}{$edges$}
\State $topologicalOrder, indegree \gets \phi, \phi$
\State $neighbors \gets ConstructNeighbors(vertices, edges)$
\For{\textbf{each} $vertex \in vertices$}
    \For{\textbf{each} $neighbor \in neighbors(vetex)$}
        \State $indegree(neighbor) \gets indegree(neighbor) + 1$
    \EndFor
\EndFor
\State $nodesWithZeroIndegree \gets \{vertex \in vertices| indegree(vertex) = 0\}$
\While{$nodesWithZeroIndegree \neq \phi$}
    \State $node \gets nodesWithZeroIndegree.\textrm{POP}()$
    \State $topologicalOrder \gets topologicalOrder \cup \{node\}$
    \For{\textbf{each} $neighbor \in neighbors(node)$}
        \State $indegree(node) \gets indegree(node) - 1$
        \If{$indegree(neighbor) = 0$}
            \State $nodesWithZeroIndegree \gets nodesWithZeroIndegree \cup \{neighbor\}$
        \EndIf
    \EndFor
\EndWhile
\State \Return $topologicalOrder$
\EndFunction

\algstore{graph}
\end{algorithmic}
\end{algorithm}

\newpage

\begin{algorithm}
\begin{algorithmic}
\algrestore{graph}

\Function{TrimGraph}{$edges$}
\State $indegree, outdegree, previousEdges \gets \phi, \phi, \phi$
\State $vertices \gets GetVerticesFromEdges(edges)$
\State $neighbors \gets ConstructNeighbors(vertices, edges)$
\For{\textbf{each} $vertex \in vertices$}
    \State $outdegree(vertex) \gets \lvert neighbors(vertex) \rvert$
    \For{\textbf{each} $neighbor \in neighbors(vetex)$}
        \State $indegree(neighbor) \gets indegree(neighbor) + 1$
    \EndFor
\EndFor
\State $nodesWithZeroIndegree \gets \{vertex \in vertices| indegree(vertex) = 0\}$
\State $nodesWithZeroOutdegree \gets \{vertex \in vertices| outdegree(vertex) = 0\}$
\While{$edges \subset previousEdges $}
\State $previousEdges \gets edges$
\While{$nodesWithZeroIndegree \neq \phi$}
    \State $node \gets nodesWithZeroIndegree.\textrm{POP}()$
    \For{\textbf{each} $neighbor \in neighbors(node)$}
        \State $indegree(node) \gets indegree(node) - 1$
        \State $outdegree(node) \gets outdegree(node) - 1$
        \If{$<node, neighbor>$}
             \State $edges.\textrm{REMOVE}(<node, neighbor>)$
        \EndIf
        \If{$indegree(neighbor) = 0$}
            \State $nodesWithZeroIndegree \gets nodesWithZeroIndegree \cup \{neighbor\}$
        \EndIf
        \If{$outdegree(node) = 0$}
            \State $nodesWithZeroOutdegree \gets nodesWithZeroOutdegree \cup \{node\}$
        \EndIf
    \EndFor
\EndWhile
\While{$nodesWithZeroOutdegree \neq \phi$}
    \State $node \gets nodesWithZeroOutdegree.\textrm{POP}()$
    \For{\textbf{each} $node' \in neighbors$}
    \If{$outdegree(node')> 0$ AND $node \in neighbors(node')$ }
    \State $outdegree(node') \gets outdegree(node') - 1$
    \State $indegree(node) \gets indegree(node) - 1$
    \If{$<node', node> \in edges$}
        \State $edges.\textrm{REMOVE}(<node', node>)$
    \EndIf
    \If{$outdegree(node') = 0$}
        \State $nodesWithZeroOutdegree \gets nodesWithZeroOutdegree \cup \{node'\}$
    \EndIf
    \If{$indegree(node) = 0$}
        \State $nodesWithZeroIndegree \gets nodesWithZeroIndegree \cup \{node\}$
    \EndIf
    \EndIf
    \EndFor
\EndWhile
\EndWhile
\State \Return $edges, indegree, outdegree$
\EndFunction

\end{algorithmic}
\end{algorithm}

\section{Source Code}

All code implementations of heuristic methods and ILP model are available at \href{https://github.com/tmactong/AMMM-project}{Github Repo}.\\
The \href{https://github.com/tmactong/AMMM-project/blob/main/README.md}{README} provides the explanation of how to use the code to solve the problem.

\end{document}